\documentclass[12pt,letterpaper]{article}
\usepackage{times}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{indentfirst}
\usepackage{wrapfig}
%\usepackage{picins}
\usepackage{alltt}
\usepackage{array}
\usepackage{siunitx}

\widowpenalty10000%
\clubpenalty10000%
\tolerance=1000

%
\newcommand{\problem}[1]{\begin{center}\section{\protect\rule{0pt}{1.1em}#1}\rhead{\sffamily\bfseries\thesection\hspace{0.5em}#1}\end{center}}
\renewcommand{\thesection}{Problem \Alph{section}:}
%\renewcommand{\sectionmark}[1]{\markright{foo #1}}
\newcommand{\verbfile}[1]{\begin{alltt}\input{#1}\end{alltt}}

\makeatletter
\renewcommand{\@seccntformat}[1]{\csname the#1\endcsname\hspace{0.5em}}

\addtolength{\headheight}{20pt}
\addtolength{\textheight}{10pt}


\lhead{}
\rhead{}
\lfoot{\sffamily\bfseries Nov.~7, 2015}
\cfoot{\sffamily\bfseries 2015 Mid-Atlantic Regional Programming Contest}
\rfoot{\sffamily\bfseries Page \thepage\ of \pageref{LastPage}}

\newenvironment{icompact}{
  \begin{list}{$\bullet$}{
    \parsep 0pt plus 1pt
    \partopsep 0pt plus 1pt
    \topsep 2pt plus 2pt minus 1pt
    \itemsep 0pt plus 1pt
    \parskip 0pt plus 2pt
    \leftmargin 0.3in}
       \raggedright}
  {\normalsize\end{list}}

\newcounter{ecount}
\newenvironment{ecompact}{
  \begin{list}{\arabic{ecount}}{\usecounter{ecount}
    \parsep 0pt plus 1pt
    \partopsep 0pt plus 1pt
    \topsep 2pt plus 2pt minus 1pt
    \itemsep 0pt plus 1pt
    \leftmargin 0.3in}
       \raggedright}
  {\normalsize\end{list}}


\pagestyle{fancy}

\begin{document}

{\sffamily
\bfseries
\Large 
\begin{center}
\protect\rule{0pt}{1.1em}2015 Mid-Atlantic Regional Programming Contest
%\\ Draft \today
\end{center}
}


This is a courtesy copy of the problem set for the
Mid-Atlantic Regional contest.  It is an abbreviated version of the
problem set provided to the teams. Omitted are several pages of rules
and explanations of the contest and judging environment.


\begin{center}
{\large\bf Important:} 
\end{center}

The creation of this problem set was a collaboration
among Regional Contests scheduled for November 7. These
contests will be starting at different times and taking place in
different time zones.

In deference to the later starting contests, we ask that you refrain
from emailing, blogging, posting, tweeting, or otherwise making any public
comments about this problem set until November 8.

~

\hrule

~

\textbf{And now, a word from the head judge}

Without a team of creative volunteers, there would be no problem set
for this contest each year.  It's not too early to start thinking
about the 2016 contest!

We do require that problem authors not be coaches of or otherwise
directly associated with a participating team. But if you are a team
coach and have a colleague who might be interested in contributing,
please drop a word to them. If you have a creative team member who
will be an alumnus or alumna next year, you might do the same.

Anyone interested in participating as a member of the authoring team
for 2016 can send their contact information to this year's head judge
for the region, Steven Zeil, at \texttt{zeil@cs.odu.edu}.

\hrule

~


\input{balloons}

\sisetup{group-separator={,}}
\input{problemList}

\end{document}
